---
title: "VAST Challenge 2021 - Mini-Challenge 3 "
description: |
  A short description of the post.
author:
  - name: Tang Yue
    url: {}
date: 07-14-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup,include=FALSE}
options(htmltools.dir.version=FALSE)
knitr::opts_chunk$set(fig.retina = 3,
                      echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

# 1. Overview

In the roughly twenty years that Tethys-based GAStech has been operating a natural gas production site in the island country of Kronos, it has produced remarkable profits and developed strong relationships with the government of Kronos. However, GAStech has not been as successful in demonstrating environmental stewardship.

In January, 2014, the leaders of GAStech are celebrating their new-found fortune as a result of the initial public offering of their very successful company. In the midst of this celebration, several employees of GAStech go missing. An organization known as the Protectors of Kronos (POK) is suspected in the disappearance, but things may not be what they seem.

On January 23, 2014, multiple events unfolded in Abila. You’ve been asked to come in to perform a retrospective analysis based on limited information about what took place. Your goal is to identify risks and how they could have been mitigated more effectively.

in this assignment we would provide some insights to help law enforcement from Kronos and Tethys.


# 2. Exploration and preparation of Data

There are two dataset provides:

(1) Microblog records that have been identified by automated filters as being potentially relevant to the ongoing incident

(2) Text transcripts of emergency dispatches by the Abila, Kronos local police and fire departments.

(3) maps of Abila and background documents.


Two dataset are stored in 3 csv files, they are csv-1700-1830.csv", "csv-1831-2000.csv' and  "csv-2001-2131.csv":

The data for Mini-Challenge 3 is found in three segments.

Segment 1 covers the time period from 1700 to 1830 Abila time on January 23. 

Segment 2 covers the time period from 1830 to 2000 Abila time on January 23. 

Segment 3 covers the time period from 2000 to shortly after 2130 Abila time on January 23. 

### 2.1 Install and load R package

First, we run the below code to set the environment.


In this assignment, the tidyverse, ggforce, GGally, plotly R and parcoords packages will be used, which could be seen from below code chunk.


```{r}
packages = c('tidyverse','dplyr','readr','tm','wordcloud','SnowballC',
             'UpSetR','ggplot2','topicmodels')
for (p in packages){
  if(!require(p, character.only = T)){
  install.packages(p)
  }
  library(p,character.only = T)
}
```


### 2.2 Import dataset and combine data

The data of Microblog records and emergency calls are stored in separate csv files. And three csv files share same columns but data generate from different date, which is shown below.

1[](image/1.files.PNG)


Firstly, we need to combine 3 files into one consolidated file, which is necessary for the following analysis. In this step, package 'tidyverse' would be used.

The following R code shows the process of data consolidation, then three dataset with different have been integrated into one file.

```{r}
library(tidyverse)
table1 <- read.csv("csv-1700-1830.csv")
table2 <- read.csv("csv-1831-2000.csv")
table3 <- read.csv("csv-2001-2131.csv")
data <- rbind(table1, table2,table3)
```


Next, we would separate 'ccdata' and 'mbdata', they represent microblog record and emergency call center data collected by  the Abila, Kronos local police and fire departments.


```{r}
ccdata <- subset(data, type == "ccdata")
mbdata <- subset(data, type == "mbdata")

```


### 2.3 Data preprocessing

### 2.3.1 Modifying Date formate  

Date data in table were shown as scientific notation, so we firstly disabling scientific notation in R for further date processing.

```{r}
library(lubridate)

options(scipen = 999)
head(data,5)

```

Next, package 'lubridate' would be used to convert data type from 'yyyymmddhhmmss' to 'yyyy-mm-dd hh:mm:ss', and create a new column 'date' in data, and the code chunk could be seen below.

```{r}
data$date <- ymd_hms(data$date.yyyyMMddHHmmss.)
head(data$date,5)
```

### 2.3.1 Text proprecessing

Steps of Text preprocessing - Text preprocessing, in general, refers to cleaning of data or making available data available for analysis so further applications like getting the frequency of words


1. Creating Corpus
 
Use the following code to load the data as a corpus. A corpus is a collection of text or speech that has been brought together according to be a certain set of predetermined criteria.   It arranges text in such a manner  so that preprocessing of data can be done or in simple words document term matrix can be created which represent each term present in the text in one hot encoding in the form of a matrix .

```{r}
report <- Corpus(VectorSource(data$message))
report

```

2. 











Next, we would use topic modeling to explore topics involved in microblog and call center records. Latent Dirichlet allocation (LDA) is a particularly popular method for fitting a topic model, here topicmodels package and present topic result with ggplot2 and dylyr.
